---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# petro.One
[![Travis-CI Build Status](https://travis-ci.org/f0nzie/petro.One.svg?branch=master)](https://travis-ci.org/f0nzie/petro.One)
[![codecov](https://codecov.io/gh/f0nzie/petro.One/branch/master/graph/badge.svg)](https://codecov.io/gh/f0nzie/petro.One)

The goal of **petro.One** is providing a reproducible platform for acquiring and analyzing metadata by searching papers on oil and gas from the OnePetro website.

## Motivation
The standard way of searching for papers in [OnePetro](https://www.onepetro.org/) is using a web browser entering the search terms for a particular paper we are looking for. The result will come as web pages containing dozens, hundreds or thousand of paper titles. We need to browse all the resulting pages to find the papers that have a good match with the subject we are researching. Although it has the capability to export to _csv_ and _xls_ files, they will need to be imported into another application to perform some analysis.

By using some statistical tools available through `R`, the search could turn in highly profitable in terms of time, matching quality and selection of the papers. The search keywords are entered thorugh the R console and the papers will return in a shape of a dataframe, which is identical to a spreadsheet: rows of paper titles and columns with details from the metadata extracted from the web page. With the dataframe already in our computers we could perform a thorough search and narrow down to the ideal papers for our research.


## Installation

You can install `petro.One` from Github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")       # install *devtools* first

# install from the *master* release branch
devtools::install_github("f0nzie/petro.One")
```

Or, the latest dvelopment version:

```{r, eval = FALSE}
# install from the *develop* branch
devtools::install_github("f0nzie/petro.One", ref = "develop")
```


Or from [CRAN](https://cran.r-project.org/) with:

```{r eval=FALSE}
install.packages("petro.One")
```

The package dependencies can be installed with:

```{r eval=FALSE}
# install required packages
# from CRAN
install.packages(c("tm",
                   "wordcloud",
                   "urltools",
                   "RWeka",
                   "tidyverse",
                   "data.table"
                   ))

# from BioConductor
source("https://bioconductor.org/biocLite.R")
biocLite("graph")
biocLite("Rgraphviz")
```


## What is behind the paper search

A typical OnePetro search URL would look like this:

        https://www.onepetro.org/search?q=neural+network&peer_reviewed=&published_between=&from_year=&to_year=
        
You can see the search string for yourself after you hit enter on a paper search, which could be explained like this:


| Parameter          | Description                                                                                                                                          |
|--------------------|------------------------------------------------------------------------------------------------------------------------------------------------------|
| domain             | https://www.onepetro.org/                                                                                                                            |
| command            | search?                                                                                                                                              |
| q=                 | parameter that holds the query words. In the example above, it would be `q=neural+network`. As it is shown, it means search `any` word. |
| peer_reviewed=     | parameter switch to get papers than have been only peer reviewed. When it has the value `on` means that is activated.                                |
| published_between= | *parameter* switch that activates when `from_year` and `to_year` have numeric entries.                                                               |
| from_year=         | *parameter* to enter the starting year of the search                                                                                                 |
| to_year=           | *parameter* to enter the end year of the search.                                                                                                     |
                                                                                

There are additional parameters such as:

| Parameter | Description                                                                                                                                                |
|-----------|------------------------------------------------------------------------------------------------------------------------------------------------------------|
| start=    | indicate the starting page if the resulting search has several                                                                                             |
| rows=     | indicate the number of rows (papers) to display per page. In the web browser, the options are 10, 50 and 100. Off-browser it could be a number up to 1000. |
| sort=     | related to the selector `Sort By` with options `Relevance`, `Most recent` and `Highest rated`.                                                             |
| dc_type=  | indicates what type of document the paper is.                                                                                                              |

These are the type of documents:

    chapter
    conference-paper
    general
    journal-paper
    presentation
    media
    other
    standard
    
There are other parameters but they will not be used as often as the ones already described.    
They key is build a search URL that is recognizable by OnePetro. To do that I wrote a function `make_search_url` that does just that. Instead of entering the search keywords, how will they be searched, year and type of paper, we enter them from the R console.

# Examples

## Get the number of papers for the keyword *neural network*.
Let's say we want to search the word **neural network**. How do we want to perform that search? Paper that contain the word **neural** or the word **network**, or papers that contain exactly the words **neural network**? In the former, we would use the option `any`, in the latter, `all`. 

The option `how = "any"` means to search for papers that contain the word `neural` or the word `network`. Let's take a look at the difference in returning results with `any` and `how = all` for the same keywords `neural network`. Here we make of use of two functions in _petro.One_:  `make_search_url()` and `get_papers_count()`.


```{r example}
library(petro.One)
library(tidyverse)

# search any word like "neural" or "network"
url_any <- make_search_url(query = "neural network", how = "any")
url_any
get_papers_count(url_any)

# search for papers that have "neural" and "network" at the same time
url_all <- make_search_url(query = "neural network", how = "all")
url_all
get_papers_count(url_all)
```


## Read papers from *from_year* to *to_year*
We can send a query where we specify the _starting year_ and the _ending year_.
In this example the option `how = "all"` means to search papers that contain **exactly** the words `neural network` as a difference to `any` which means search for `any` occurrence of the words. Of course, using `any` rather than `all` will yield many more results.
We use two petro.One functions: `make_search_url()` to build the OnePetro search URL and `onepetro_page_to_dataframe()` to put the papers in a table.

```{r}
library(petro.One)

# neural network papers from 1990 to 1999. Exact phrase
my_url <- make_search_url(query = "neural network", 
                          from_year = 1990, 
                          to_year   = 1999, 
                          how = "all")

df <- onepetro_page_to_dataframe(my_url)
df
```

And these are the terms that repeat more freqently:

```{r}
term_frequency(df)
```



## Get papers by document type (*dc_type*)
We can also get paper by the type of document. In OnePetro it is called `dc_type`.

In this example we will be requesting only `conference-paper` type.
Here we add to `make_search_url()` the parameter `dc_type`. Note also that we are adding another parameter `rows` to get 1000 rows instead of 10, 50 or 100 as the browser allows.

```{r}
# specify document type = "conference-paper", rows = 1000

my_url <- make_search_url(query = "artificial intelligence", 
                          how = "all",
                          from_year = 1950, 
                          to_year   = 1980, 
                          dc_type = "conference-paper",
                          rows = 1000)

(pcount <- get_papers_count(my_url))
df <- onepetro_page_to_dataframe(my_url)
df
```

Only `r pcount` on _artificial intelligence_ from 1950 until 1980!


## Finding the most frequent terms in *well test*
For this example we want to know about _conference papers_ where the words *well* and *test* are found together in the papers.

```{r welltest}
library(petro.One)

my_url <- make_search_url(query = "well test", 
                          dc_type = "conference-paper",
                          from_year = 2017, 
                          to_year   = 2018, 
                          how = "all")

get_papers_count(my_url)      # get the paper count
df <- read_multidoc(my_url)   # create a dataframe of papers
print(dim(df))                # dimension of the dataframe

(tf <- term_frequency(df))    # create a term frequency table

# calculate the minimum frequency for, let's say, the first 20th term
min_freq <- min(head(tf, 20)$freq)
```

### Most frequent terms in *well test*

```{r}
print(min_freq)
# plot most frequent terms
plot_bars(df, min.freq = min_freq)
```

### How do the most frequent terms relate each other
Now, it is not enough for us to know what terms are the more repeating but how those freqent terms relate to each other. In the following plot you will see that the strength of the relationship between terms is reflected by the thickness of the connection lines.

```{r}
plot_relationships(df, min.freq = min_freq, threshold = 0.075)
```

We can see that *wells* and *well* are connected strongly to *horizontal*, *transient*, *pressure*, *flow*, *testing*, *reservoirs*, *fracture*, and *analysis*. The rest of the words are frequent but not very much connected.



## Summaries
The summary functions allow us to group the papers by a preferred group:

* by type of document
* by publisher
* by publication
* by year

This will give you a summary of the count not the papers themselves.

```{r}
library(petro.One)

my_url <- make_search_url(query = "artificial intelligence", 
                          how = "all")
```

### By year of publication

```{r, echo=FALSE, results='asis'}
pby <- papers_by_year(my_url)
knitr::kable(head(pby, 10))
```



# Text Mining

## Providing multiple keywords

```{r}
library(petro.One)
library(tidyverse)

# provide two different set of keywords to combine as vectors
major   <- c("artificial intelligence")

paper_results <- run_papers_search(major, 
                                   get_papers = TRUE,       # return with papers
                                   verbose = FALSE,         # show progress
                                   len_keywords = 4,        # naming the data file
                                   allow_duplicates = FALSE) # by paper title and id

(papers <- paper_results$papers)
```

```{r}
# plot on AI by year of publication
papers %>% 
    group_by(year) %>% 
    na.omit() %>% 
    summarize(n = n()) %>% 
    
    ggplot(., aes(x = year, y = n)) +
    geom_point() +
    geom_smooth(method = "loess") +
    labs(title = "Artificial Intelligence papers by Year")
```

```{r}
tf <- term_frequency(papers)
tf
```

```{r}
# one word or gram
term_frequency_n_grams(df = papers, gram.min = 1, gram.max = 1)
```


```{r}
# calculate the minimum frequency for, let's say, the first 20th term
(min_freq <- min(head(tf, 20)$freq))
```

```{r}
# plot the most frequent terms
plot_bars(papers, min.freq = min_freq)
```

```{r}
# by default the number of grams is two (2)
tf2 <- term_frequency_n_grams(papers)
tf2
```


```{r}
plot_bars(papers, min.freq = 100)
```

```{r}
# plot for two-grams
plot_bars(papers, gram.min = 2, gram.max = 2, min.freq = 35)
```

```{r}
# plot for three-grams
plot_bars(papers, gram.min = 3, gram.max = 3, min.freq = 12)
```
