---
title: "R Notebook"
output: html_notebook
---

```{r make-the-function}
library(rvest)
library(dplyr)
library(petro.One)

get_dc_type <- function(page_size) {
    url <- "https://www.onepetro.org/search?start=0&q=pressure&from_year=&peer_reviewed=&published_between=&to_year=&rows="
    
    url <- paste0(url, page_size)
    webpage <<- xml2::read_html(url)
    
    dc_type_0 <- html_nodes(webpage, '.result-item') %>%
     html_attr("data-type") %>% 
    trimws %>% 
    head(., -1)
    
    col2 <- html_nodes(webpage, '.result-item') %>%
        html_attr("data-itemid") %>% 
        gsub("data-cite-id=", "", .) %>% 
        trimws %>% 
        head(., -1)
    
    # col2_df <- data.frame(do.call(rbind, strsplit(col2, "/")), stringsAsFactors = FALSE)
    col2_split <- strsplit(col2, "/")
    col2_df <- data.frame(t(sapply(col2_split, '[', 1:max(sapply(col2_split, length)))),
                          stringsAsFactors = FALSE)
    
    dc_type <- col2_df %>%
        rename(dc_type_1 = X1, paper_id = X2, dc_type_2 = X3, sup = X4) %>%
        mutate(x1x3 = ifelse(dc_type_1 == dc_type_2, TRUE, FALSE)) %>%
        mutate(dc_type = ifelse(dc_type_2 %in% "SUPPLEMENTARY", "media", dc_type_1)) %>% 
        mutate(dc_type = ifelse(dc_type_1 %in% "book", "chapter", dc_type))
    
    # number of columns of result is not a multiple of vector length (arg 154)
    # cbind(dc_type, result_item_source)
    tibble::as.tibble(cbind(dc_type_0, dc_type))
}
```



```{r}
dc_type <- get_dc_type(100)
dc_type
```

```{r}
unique(dc_type$dc_type)
```


## Get a glipmse of the number of paper by type
* Pay special attention to papers of type: `media`, `chapter`, `other`
* Also observe that the total number of papers must be the same as sum of all types.

```{r dc_type_table_sum}
dc_type <- get_dc_type(100)

dc_type %>% 
    group_by(dc_type) %>% 
    summarise(count = n())

sum(.Last.value$count)
# page_size, media  chapter other
#  100          1       0     2     100
#  200          6       0           200
#  300          6       0
#  400          6       1           400
#  500          6       1
#  600          7       2   20       600
#  700         12       2
#  800         16       3
# 1000         16       3
```

`Titles` are not the same size as `dc_type` above. Why?

```{r titles_do_not_match_dc-type}
df.titles <- petro.One:::read_titles(webpage)
dim(df.titles)
# 600 573   1
# 100  97   1

```

This will give error because columns are different

```{r}
df.sources <- petro.One:::read_sources(webpage)
unique(df$type)
# error:
# number of columns of result is not a multiple of vector length (arg 69)
```

## Let's try to get the titles in another way


```{r function-get_book_title}
get_book_title <- function(webpage) {
    html_nodes(webpage, '.result-item') %>%
        html_nodes(".book-title") %>% 
        html_text %>% 
        gsub("\n", "", .) %>% 
        trimws
}

get_book_title(webpage)
```

### merge titles and dc_type
It they match, ther shouldn't be any error

```{r form_book_title, rows.print=25}
dc_type <- get_dc_type(100)
book_title <- get_book_title(webpage)
tibble::as.tibble(cbind(book_title, dc_type))
```

## Get the authors

```{r function-get_book_title}

dc_type <- get_dc_type(100)
# book_title <- get_book_title(webpage)
# cbind(book_title, dc_type)

get_result_item_authors <- function(webpage) {
    html_nodes(webpage, '.result-item') %>%
        # html_nodes(".result-item-authors")
        html_nodes(".highlighted") %>% 
        html_text %>% 
        #gsub("\n", "", .) %>% 
        trimws %>%     
        strsplit("\n") %>% 
        lapply(., trimws) %>% 
        lapply(., function(x) x[!x %in% ""])  # remove a blank from a list
    
}

item_authors <- get_result_item_authors(webpage)
lapply(item_authors, function(x) x[1:2])
```

```{r}
#item_authors
#grepl("[,.]", item_authors[[1]][1])

# is the first element of the list a name? Because it contains dot and commas
sapply(1:100, function(x) grepl("[,.].", item_authors[[x]][1]))

```

```{r}
# no comma
item_authors[[5]]
```

```{r}
# one comma stand-alone
item_authors[[71]]
```

```{r}
# one comma stand-alone
item_authors[[70]]
```

```{r rows.print=30}
get_authors <- function() {
    data.frame(authors = sapply(1:100, join_authors), stringsAsFactors = FALSE)
}


#' @param x called by apply function
join_authors <- function(x) {
    nm1 <- if (grepl("[,.]", item_authors[[x]][1])) item_authors[[x]][1] else "NA"
    nm2 <- if (grepl("[,.]", item_authors[[x]][2]) & nm1 != "NA") item_authors[[x]][2] else "NA"
    nm3 <- if (grepl("[,.]", item_authors[[x]][3]) & nm2 != "NA") item_authors[[x]][3] else "NA"
    nm4 <- if (grepl("[,.]", item_authors[[x]][4]) & nm3 != "NA") item_authors[[x]][4] else "NA"
    nm5 <- if (grepl("[,.]", item_authors[[x]][5]) & nm4 != "NA") item_authors[[x]][5] else "NA"
    nm6 <- if (grepl("[,.]", item_authors[[x]][6]) & nm5 != "NA") item_authors[[x]][6] else "NA"
    nm7 <- if (grepl("[,.]", item_authors[[x]][7]) & nm6 != "NA") item_authors[[x]][7] else "NA"
    nm8 <- if (grepl("[,.]", item_authors[[x]][8]) & nm7 != "NA") item_authors[[x]][8] else "NA"
    authors <- paste(nm1, nm2, nm3, nm4, nm5, nm6, nm7, nm8, sep = "|")
    authors <- strsplit(authors, "|", fixed = TRUE)
    authors <- lapply(authors, function(x) x[!x %in% "NA"] )  # remove a blank from a list
    authors <- sapply(authors, paste, collapse = " | ")
    if (is_author(authors)) authors else "unknown"
}



# how many times a character repeats
# we wantr to find only occurance of only one comma. It means it is not a name
# and probably empty. Names have at least two commas
character_repeats <- function(char_vector, the_char = ",") {
    sapply(gregexpr(",", char_vector), function(x) length(x))
}


# logical. if the count os greater than one, it is a name.
# if the count is one or zero, then
is_author <- function(author_vector) {
    stopifnot(!is.numeric(author_vector))
    repeats <- character_repeats(author_vector)
    ifelse(repeats > 1, TRUE, FALSE)
}

authors <- get_authors()
authors
```

## Merge titles, dc-types and authors

```{r form_authors_title_dc-type, rows.print=25}
dc_type <- get_dc_type(100)
book_title <- get_book_title(webpage)
tibble::as.tibble(cbind(book_title, dc_type, authors))
```

```{r}
item_authors[1:10]
```

Get all years from the list

```{r}
rapply(item_authors, grep, pattern = "- [0-9].", perl = TRUE, value= TRUE)
```

```{r}
f <- function(x) {
    if (!any(sapply(x, function(y) grepl(y, pattern = "- [0-9].", perl = TRUE))))
        NA
    else {
        as.integer(trimws(gsub("-", "",grep(x, pattern = "- [0-9].", perl = TRUE, value = TRUE))))
    }
        
}

data.frame(year = sapply(item_authors, f))

```

## Merge titles, authors, dc-type, year

```{r form_authors_title_dc-type, rows.print=25}
dc_type <- get_dc_type(100)
book_title <- get_book_title(webpage)
year <- get_year(item_authors)
cbind(book_title, dc_type, authors, year)
```

## get the source or publication

```{r}
item_authors[1:10]
```



```{r}
f <- function(x) {
    if (!any(sapply(x, function(y) grepl(y, pattern = "^[A-Z]+$", perl = TRUE))))
        NA
    else
        grep(x, pattern = "^[A-Z]+$", perl = TRUE, value = TRUE)
}

sapply(item_authors, f)
```


## Merge titles, authors, year, dc-type, source

```{r rows.print=30}
dc_type <- get_dc_type(300)
book_title <- get_book_title(webpage)
item_authors <- get_result_item_authors(webpage)
year <- get_year(item_authors)
source <- get_source(item_authors)
cbind(book_title, dc_type, authors, year, source)
```

## downloads

```{r}
# downloads
dc_type <- get_dc_type(100)
book_title <- get_book_title(webpage)

pattern <- "[0-9.]+(?= downloads)"

f <- function(x) {
    sapply(x, function(y) grep(pattern, y, perl = TRUE))
}

sapply(item_authors, f)
```
