---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rvest)
library(dplyr)
library(petro.One)
```


```{r}
url <- "https://www.onepetro.org/search?start=0&q=pressure&from_year=&peer_reviewed=&published_between=&to_year=&rows="

make_webpage_of_size <- function(url, page_size) {
    url <- paste0(url, page_size)         # join the number of rows to the URL
    xml2::read_html(url)
}

webpage_100 <- make_webpage_of_size(url, 100)
```



```{r}
get_dc_type <- function(webpage) {
    
    dc_type_0 <- html_nodes(webpage, '.result-item') %>%
        html_attr("data-type") %>% 
        trimws %>%         # remove blanks
        head(., -1)        # discard last row
    
    col2 <- html_nodes(webpage, '.result-item') %>%
        html_attr("data-itemid") %>% 
        gsub("data-cite-id=", "", .) %>% 
        trimws %>% 
        head(., -1)
    
    # col2_df <- data.frame(do.call(rbind, strsplit(col2, "/")), stringsAsFactors = FALSE)
    col2_split <- strsplit(col2, "/")
    col2_df <- data.frame(t(sapply(col2_split, '[', 1:max(sapply(col2_split, length)))),
                          stringsAsFactors = FALSE)
    
    dc_type <- col2_df %>%
        rename(dc_type_1 = X1, paper_id = X2, dc_type_2 = X3, sup = X4) %>%
        mutate(x1x3 = ifelse(dc_type_1 == dc_type_2, TRUE, FALSE)) %>%
        mutate(dc_type = ifelse(dc_type_2 %in% "SUPPLEMENTARY", "media", dc_type_1)) %>% 
        mutate(dc_type = ifelse(dc_type_1 %in% "book", "chapter", dc_type))
    
    # number of columns of result is not a multiple of vector length (arg 154)
    # cbind(dc_type, result_item_source)
    tibble::as.tibble(cbind(dc_type_0, dc_type))
}
```


```{r}
webpage <- webpage_100

data_itemid <- html_nodes(webpage, '.result-item') %>%
    html_attr("data-itemid") %>%      # extract data-itemid
    gsub("data-cite-id=", "", .) %>% 
    trimws %>% 
    head(., -1)



head(data_itemid)
```

```{r get_data_itemid}
get_data_itemid <- function(webpage) {
    data_itemid <- html_nodes(webpage, '.result-item') %>%
    html_attr("data-itemid") %>%      # extract data-itemid
    gsub("data-cite-id=", "", .) %>% 
    trimws %>% 
    head(., -1)
    
    data_itemid <- strsplit(data_itemid, "/")
    data.frame(t(sapply(data_itemid, '[', 1:max(sapply(data_itemid, length)))), 
               stringsAsFactors = FALSE)
}


get_data_itemid(webpage)
```


```{r get_dc_type-p1}
get_dc_type_raw <- function(webpage) {
    
    dc_type_0 <- html_nodes(webpage, '.result-item') %>%
        html_attr("data-type") %>% 
        trimws %>%         # remove blanks
        head(., -1)        # discard last row
    
    data_itemid <- get_data_itemid(webpage)
    
    dc_type <- data_itemid %>%
        rename(dc_type_1 = X1, paper_id = X2, dc_type_2 = X3, sup = X4) %>%
        mutate(x1x3 = ifelse(dc_type_1 == dc_type_2, TRUE, FALSE)) %>%
        mutate(dc_type = ifelse(dc_type_2 %in% "SUPPLEMENTARY", "media", dc_type_1)) %>% 
        mutate(dc_type = ifelse(dc_type_1 %in% "book", "chapter", dc_type))
    
    # number of columns of result is not a multiple of vector length (arg 154)
    tibble::as.tibble(cbind(dc_type_0, dc_type))
}

dc_type_raw <- get_dc_type_raw(webpage)
dc_type_raw
```

```{r get_dc_type}
get_dc_type <- function(webpage) {
    dc_type_raw <- get_dc_type_raw(webpage)
    dc_type_raw$dc_type
}

dc_type <- get_dc_type(webpage)
dc_type
```













```{r}
unique(dc_type)
```


## Get a glipmse of the number of paper by type
* Pay special attention to papers of type: `media`, `chapter`, `other`
* Also observe that the total number of papers must be the same as sum of all types.

```{r dc_type_table_sum}
dc_type <- data.frame(dc_type = get_dc_type(webpage))

dc_type %>% 
    group_by(dc_type) %>% 
    summarise(count = n())

sum(.Last.value$count)
# page_size, media  chapter other
#  100          1       0     2     100
#  200          6       0           200
#  300          6       0
#  400          6       1           400
#  500          6       1
#  600          7       2   20       600
#  700         12       2
#  800         16       3
# 1000         16       3
```

## Titles

`Titles` are not the same size as `dc_type` above. Why?

```{r titles_do_not_match_dc-type}
df.titles <- petro.One:::read_titles(webpage)
dim(df.titles)
# 100  97   1
# 600 573   1
# 100  97   1

```

This will give error because columns are different

```{r}
df.sources <- petro.One:::read_sources(webpage)
unique(df$type)
# error:
# number of columns of result is not a multiple of vector length (arg 69)
```

### Let's try to get the titles in another way

```{r function-get_book_title}
get_book_title <- function(webpage) {
    html_nodes(webpage, '.result-item') %>%
        html_nodes(".book-title") %>% 
        html_text %>% 
        gsub("\n", "", .) %>% 
        trimws
}

get_book_title(webpage)
```

### merge titles and dc_type
It they match, ther shouldn't be any error

```{r merge-book_title-dc_type, rows.print=25}
dc_type <- get_dc_type(webpage)
book_title <- get_book_title(webpage)
tibble::as.tibble(cbind(book_title, dc_type))
```

## Authors


```{r function-get_authors}

get_result_item_authors <- function(webpage) {
    html_nodes(webpage, '.result-item') %>%
        # html_nodes(".result-item-authors")
        html_nodes(".highlighted") %>% 
        html_text %>% 
        #gsub("\n", "", .) %>% 
        trimws %>%     
        strsplit("\n") %>% 
        lapply(., trimws) %>% 
        lapply(., function(x) x[!x %in% ""])  # remove a blank from a list
    
}


get_authors <- function(webpage) {
    #' @param x called by apply function
    join_authors <- function(x, y) {
        nm1 <- if (grepl("[,.]", y[[x]][1])) y[[x]][1] else "NA"
        nm2 <- if (grepl("[,.]", y[[x]][2]) & nm1 != "NA") y[[x]][2] else "NA"
        nm3 <- if (grepl("[,.]", y[[x]][3]) & nm2 != "NA") y[[x]][3] else "NA"
        nm4 <- if (grepl("[,.]", y[[x]][4]) & nm3 != "NA") y[[x]][4] else "NA"
        nm5 <- if (grepl("[,.]", y[[x]][5]) & nm4 != "NA") y[[x]][5] else "NA"
        nm6 <- if (grepl("[,.]", y[[x]][6]) & nm5 != "NA") y[[x]][6] else "NA"
        nm7 <- if (grepl("[,.]", y[[x]][7]) & nm6 != "NA") y[[x]][7] else "NA"
        nm8 <- if (grepl("[,.]", y[[x]][8]) & nm7 != "NA") y[[x]][8] else "NA"
        authors <- paste(nm1, nm2, nm3, nm4, nm5, nm6, nm7, nm8, sep = "|")
        authors <- strsplit(authors, "|", fixed = TRUE)
        authors <- lapply(authors, function(x) x[!x %in% "NA"] )  # remove a blank from a list
        authors <- sapply(authors, paste, collapse = " | ")
        #if (is_author(authors)) authors else "unknown"
    }
    
    item_authors <- get_result_item_authors(webpage)
    data.frame(authors = sapply(seq_along(item_authors), join_authors, item_authors),
               stringsAsFactors = FALSE)
}

get_authors(webpage)
```

```{r merge-dc_type-book_title-authors}
dc_type    <- get_dc_type(webpage)
book_title <- get_book_title(webpage)
authors    <- get_authors(webpage)
tibble::as.tibble(cbind(book_title, dc_type, authors))
```

## Year

```{r get_year}

get_year <- function(webpage) {
    f <- function(x) {
        if (!any(sapply(x, function(y) grepl(y, pattern = "- [0-9].", perl = TRUE))))
            NA
        else {
            as.integer(trimws(gsub("-", "",grep(x, pattern = "- [0-9].", perl = TRUE, value = TRUE))))
        }

    }
    item_authors <- get_result_item_authors(webpage)
    data.frame(year = sapply(item_authors, f))
}


get_year(webpage)

```

## Sources

```{r get_source}
get_source <- function(webpage) {
    f <- function(x) {
        if (!any(sapply(x, function(y) grepl(y, pattern = "^[A-Z]+$", perl = TRUE))))
            NA
        else
            grep(x, pattern = "^[A-Z]+$", perl = TRUE, value = TRUE)
    }
    item_authors <- get_result_item_authors(webpage)
    sapply(item_authors, f)
}

get_source(webpage)
```

## Merge all

```{r rows.print=25, merge-dc_type-book_title-authors-year-source}
dc_type    <- get_dc_type(webpage)
book_title <- get_book_title(webpage)
authors    <- get_authors(webpage)
year       <- get_year(webpage)
source     <- get_source(webpage)

tibble::as.tibble(cbind(book_title, dc_type, authors, year, source))
```












