---
title: "Reducing paper results by joining keywords"
author: "Alfonso R. Reyes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a demonstration on how the number of papers can be reduced using additional keywords to control the number of results returned.

```{r}
library(petro.One)
```


## test #1
We start with these keywords:
    water injection     water flooding
    machine-learning    artificial intelligence
    neural networks

```{r, 5-keywords}
# provide two different set of keywords to combine as vectors
major  <- c("water injection", "water flooding")
minor  <- c("machine-learning", "artificial intelligence")
lesser <- c("neural networks")

result_object <- join_keywords(major, minor, lesser, get_papers = TRUE)
result_object
```


```{r}
# save findings
# save the three objects as one
papers <- result_object
wat_inj_ml_1 <- petro.One:::as_named_list(major, minor, lesser, papers)
save(wat_inj_ml_1, file = paste0("wat_inj_ml_1", ".rda"))

# load previous save
load(file = paste0("wat_inj_ml_1", ".rda"))
papers <- wat_inj_ml_1$papers
papers
```

## Using a new function to replace multiple commands

```{r}
paper_results <- run_papers_search(major, minor, lesser,
                                   get_papers = TRUE,       # return with papers
                                   verbose = FALSE,         # show progress
                                   len_keywords = 4,        # naming the data file
                                   allow_duplicates = FALSE) # by paper title and id
```

```{r}
names(paper_results)
```



### test #2
Then, we increase the number of keywords:

    water injection     water flooding
    machine-learning    machine learning    intelligent
    neural network      SVM                 genetic
    algorithm

```{r}
# provide two different set of keywords to combine as vectors
m  <- c("water injection", "water flooding")
n  <- c("machine-learning", "machine learning", "intelligent")
p  <- c("neural network", "SVM", "genetic")
q  <- c("algorithm")

paper_results_9 <- run_papers_search(m, n, p, q,
                                   get_papers = TRUE,       # return with papers
                                   verbose = FALSE,         # show progress
                                   len_keywords = 4,        # naming the data file
                                   allow_duplicates = FALSE) # by paper title and id

paper_results_9$papers
```



## Reducing test 5.2

      waterflooding
      machine-learning    artificial intelligence
      algorithm
      data-mining
      data-driven

```{r, 6-keywords}
# provide two different set of keywords to combine as vectors
maj <- c("waterflooding")
min <- c("machine-learning", "artificial intelligence")
les <- c("algorithm")
anr <- c("data-mining", "data-driven")

paper_results_5 <- run_papers_search(maj, min, les, anr, 
                                   get_papers = TRUE,       # return with papers
                                   verbose = FALSE,         # show progress
                                   len_keywords = 4,        # naming the data file
                                   allow_duplicates = FALSE) # by paper title and id

paper_results_5$keywords
```

```{r}
paper_results_5$search_keywords
```

