---
title: "R Notebook"
output: html_notebook
---

We start by providing the keywords or words that are key for finding what we are searching.

```{r}
library(petro.One)
url_any <- make_search_url(query = "Cantarell", how = "any")
get_papers_count(url_any)
```

Papers that differ in how "cantarell" is spelled:

```{r}
url_any <- make_search_url(query = "Cantarel", how = "any")
get_papers_count(url_any)
```

Only one paper with Cantarell and Optimization

```{r}
library(petro.One)
url_any <- make_search_url(query = "Cantarell optimization", how = "all")
get_papers_count(url_any)
```

UK english spelling of "optimization":

```{r}
library(petro.One)
url_any <- make_search_url(query = "Cantarell optimisation", how = "all")
get_papers_count(url_any)
```

Any keywords "network"

```{r}
library(petro.One)
url_any <- make_search_url(query = "Cantarell network", how = "all")
get_papers_count(url_any)
```

## Provide keywords
In this example we provide a list of keywords as a text list - later converted to a dataframe-, that is used by petro.One to iterate through that list of keywords.


```{r}
library(petro.One)

# provide the list of keywords
keywords <- "    
    Cantarell
    Cantarell optimization
    Cantarell optimisation
    Cantarell modeling
    Cantarell modelling
    Cantarell network
    Cantarell increase
    Cantarell production
    Cantarell IPM
    Cantarell integrated
    Cantarell gain
    Cantarell pipesim
"
# convert the text to a dataframe
#
# keywords
# read.table(text = keywords, header = FALSE, allowEscapes = FALSE)
# read text table and split rows at carriage return
kw_tbl <- read.table(text = keywords, header = FALSE, 
                              sep = "\n", stringsAsFactors = FALSE, 
                     strip.white = TRUE)
kw_tbl
```


```{r rows.print = 20}
rec <- vector("list")
i <- 1
for (k in kw_tbl$V1) {
    url_all <- make_search_url(query = k, how = "all")
    count <- get_papers_count(url_all)
    rec[[i]] <- list(keyword = k, count = count)
    cat(sprintf("%30s %5d \n", k, count))
    i <-  i + 1
    Sys.sleep(5)
}
data.table::rbindlist(rec)
```





```{r}
library(petro.One)
url <- make_search_url(query = "Cantarell production", how = "all")
df1 <- onepetro_page_to_dataframe(url)
df1
```

```{r}
library(petro.One)
url <- make_search_url(query = "Cantarell optimization", how = "all")
df2 <- onepetro_page_to_dataframe(url)
df2
```

## Another way to do it: by getting the list of all papers

```{r}
library(petro.One)
url <- make_search_url(query = "Cantarell", how = "all", rows = 1000)
df <- onepetro_page_to_dataframe(url)
df
```
