

# Analysis

```{r}
library(dplyr)

# get data file from package folder
results_loc <- system.file("results", package = "petro.One")
load(file = paste(results_loc, "ml_technique_4.rda", sep = "/"))

# get dataframes
keywords.5 <- by.ml_technique.4$keywords
papers.5   <- by.ml_technique.4$papers

# sort and sum most used algos
keywords.5 %>%
    group_by(Var3) %>%
    summarize(papers=sum(paper_count)) %>%
    rename(algorithm = Var3) %>% 
    arrange(desc(papers))

```

> Note. The resulting papers in the summary does not consider there are duplicate papers.

### Create a unique `uid` for all the papers
This step will allow us to distinguish between duplicate papers.
Note that the total number of papers is above 8600.

```{r}
# papers with three columns only
new.papers.5 <- papers.5 %>% 
    select(title_data, keyword, year, paper_id, source) %>% 
    mutate(id = trimws(paste0(trimws(source), trimws(paper_id))))

new.papers.5
```

### non duplicate papers


```{r}
# how many duplicate papers
new.papers.5 %>% 
    distinct(id, title_data)

# with id only was 744
```


### split the keyword variable





```{r}
# split keyword at AND word
res <- strsplit(new.papers.5$keyword, "AND")
res[[1]]

# replace extraneous chars by blank and space in str string vectors 
res.la.1 <- lapply(res, function(x) gsub("\\+", " ", x))
res.la.2 <- lapply(res.la.1, function(x) gsub("'", "", x))
res.la.2[[1]]

# convert list of string vectors to dataframe
keyword.cols <- as.data.frame(do.call(rbind, res.la.2), stringsAsFactors = FALSE)
keyword.cols

# merge columns
mod.papers.5 <- cbind(new.papers.5, keyword.cols)
mod.papers.5
```


```{r}
# save dataframe to development results
devres_loc <- "../inst/results"
write.csv(mod.papers.5, file = paste(devres_loc, "ml_papers_5.csv", sep = "/"))
```


```{r}
baseline <- ""
recno <- 1
for (i in mod.papers.5$id) {
    
    #cat(recno, baseline, i, "\n")
    if (i != baseline) {
        cat(recno, i, baseline, "\n")
        Sys.sleep(3)
        
    }
    baseline <- mod.papers.5$id[recno]
    recno <- recno + 1
}
```


```{r}
library(dplyr)
mod.papers.5 %>%
    distinct(title_data, id)
```

```{r}
names(mod.papers.5)
```

```{r}
# get row index number for non-duplicated rows
nodup.papers.5 <- mod.papers.5[!duplicated(mod.papers.5[6]),]
nodups.papers.5 <- nodup.papers.5 %>% 
    select(-c(keyword, paper_id, source, V1))
```

```{r}
# save dataframe to development results
devres_loc <- "../inst/results"
write.csv(nodups.papers.5, file = paste(devres_loc, "ml_nodups_papers_5.csv", sep = "/"))
```



## Read Excel file with Petroleum Engineering applications
The Excel file has been manually modified by the user to enter which petroleum engineering discipline the paper belongs to. This is a very tiring activity since the user has to go paper by paper and find whichdiscipline falls into.

```{r}
# read the user modified Excel file with PE discipline assignment
devres_loc <- "../inst/results"
xls.nodups.papers.4 <- readxl::read_xlsx(paste(devres_loc, "ml_nodups_papers_4.xlsx", sep = "/"), sheet = 1)
xls.nodups.papers.4
```

```{r}
# unique PE applications
unique(xls.nodups.papers.4$pe_app)
```


```{r}
library(dplyr)

# group by application and algorithm
grouped.5 <- xls.nodups.papers.4 %>% 
    select(-c(X__1)) %>% 
    group_by(pe_app, V3) %>% 
    summarize(avg_count = n()) %>% 
    arrange(desc(V3)) %>% 
    print
```

