---
title: "R Notebook"
output: html_notebook
---







And plot a wordcloud:

```{r fig.height=9, fig.width=6}
plot_wordcloud(df, max.words = 100, min.freq = 10)
```

#### Journal papers (`journal-paper`)
In this other example we are requesting for `journal-paper` type of papers. We are also specifying to get the maximum number of rows that OnePetro permits per page: 1000. Of course, this value is not shown in the rows by page selector which maxes out at 100. It is understandable because loading 1000-row page would take too long.

```{r}
# specify document type = "journal-paper", rows = 1000

my_url <- make_search_url(query = "neural network", 
                          how = "all",
                          dc_type = "journal-paper",
                          rows = 1000)

get_papers_count(my_url)
df <- onepetro_page_to_dataframe(my_url)
df
```

#### Word cloud for journal papers

```{r fig.height=9, fig.width=6}
plot_wordcloud(df, max.words = 100, min.freq = 50)
```




## Stronger term relationships

For instance, if you are looking for papers that have stronger relationship between *well test* and *permeability*, it would wise to add that term to the search.

```{r}
library(petro.One)

my_url <- make_search_url(query = "well test permeability", 
                          dc_type = "conference-paper",
                          how = "all")

get_papers_count(my_url)
df <- read_multidoc(my_url)

term_frequency(df)
plot_bars(df, min.freq = 10)
```

In this example, we can see the effect of refining our search by including the term *permeability*.

```{r}
plot_relationships(df, min.freq = 15, threshold = 0.05)
```

This has the advantage of improving the search and narrow down the papers we are more interested in.





Here is an example of summaries. In this case, we want papers that contain the exact words "well test".

```{r}
library(petro.One)

my_url <- make_search_url(query = "well test", 
                          how = "all")
```

```{r eval=FALSE}
papers_by_type(my_url)
```


### By document type
```{r, echo=FALSE, results='asis'}
knitr::kable(papers_by_type(my_url))
```


### By publisher
```{r eval=FALSE}
papers_by_publisher(my_url)
```

```{r, echo=FALSE, results='asis'}
knitr::kable(head(papers_by_publisher(my_url), 10))
```

### By publication source

```{r eval=FALSE}
papers_by_publication(my_url)
```

```{r, echo=FALSE, results='asis'}
knitr::kable(head(papers_by_publication(my_url), 10))
```





## Search for **any** word
In this other example, we want papers that containg the word "well" or "test".

```{r}
library(petro.One)

my_url <- make_search_url(query = "well test", 
                          how = "any")

by_doctype <- papers_by_type(my_url)
```

```{r eval=FALSE}
by_doctype
```

```{r, echo=FALSE, results='asis'}
knitr::kable(by_doctype)
```


#### Total number of papers that contain **well** or **test**
In this example we get the total number of papers by document type.

```{r}
sum(by_doctype$value)
```

Or use the R base function `summary` to give us a quick statistics of the papers:

```{r}
# r-base function summary
summary(by_doctype)
```
